A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-22 0_main.tex
forgot to actually add the new section
redo overview
fix order of chapters
change title

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

@@

	\newlength{\figwidth}
	\newlength{\figheight}
	\newlength{\figheightTwo}

@@

%\title{A robust framework for variable extrusion width concentric toolpath generation}
\title{A parametric system for adaptive extrusion width contour parallel toolpath generation}

@@

>>>>

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage[draft]{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

@@

	\newlength{\figwidth}
	\newlength{\figwidthTwo}
	\newlength{\figwidthTree}
	\newlength{\figheight}
	\newlength{\figheightTwo}
	\newlength{\tempheight}
	\newlength{\tempheightTwo}

@@

%\title{A robust framework for variable extrusion width concentric toolpath generation}
\title{A parametric system for generating contour parallel toolpaths with adaptive extrusion width}

@@

\input{5_generalization}
